An Imaging Search for Post-MS Companions of Sirius B

### 2021-12-07 paper/paper.tex
tidy tex
Updates from Overleaf

% custom SI units
\DeclareSIUnit\parsec{pc}
\DeclareSIUnit\au{AU}
\DeclareSIUnit\jupitermass{M_J}
\DeclareSIUnit\milliarcsecond{mas}
\DeclareSIUnit\solarmass{M_\odot}
\DeclareSIUnit\year{yr}
\DeclareSIUnit\pixel{px}
\sisetup{
    list-units=single,
    separate-uncertainty,
    separate-uncertainty-units=single,
}

@@

\received{August 13, 2021}
\revised{\today}

@@

\title{An Imaging Search for Post-Main-Sequence Planets of Sirius B}

\shorttitle{An Imaging Search for Post-MS Planets of Sirius B}
\shortauthors{Lucas et al.}

@@

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf, to constrain post-main-sequence planetary evolution in the Sirius system. We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. Our observations are speckle-limited out to \qty{1}{\au} and background-limited beyond. The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} \Lp absolute magnitude. We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits, and achieve sub-Jupiter sensitivities at sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}. Consistent with previous results, we do not detect any companions around Sirius B. Our strong detection limits demonstrate the potential of using high-contrast imaging to characterize nearby white dwarfs.
\end{abstract}

@@

In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}. The eventual fate of planets around these stars is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}. Despite this, evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought. Discovery and characterization of post-MS planets is essential to study how they transform and how they interact with their hosts during the most critical phases of stellar evolution.

The post-MS lifetimes of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs. As the main-sequence star runs out of hydrogen to burn in its core, it expands to hundreds of times its size, engulfing any companions within the stellar radius. When helium fusion ignites, the giant star becomes three to four orders of magnitude brighter, causing stellar winds and strong irradiation. Eventually, the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf. The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet to survive around a post-MS host is violent and uncertain. During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Planets which survive their hosts' inflation are privy to the effects of stellar winds and the high luminosities of asymptotic giant stars \citep{mustillForetellingsRagnarokWorldengulfing2012,mustillMainsequenceProgenitorConfigurations2013,verasPostmainsequencePlanetarySystem2016}. The stellar winds will chemically enrich the circumstellar environment with metals and dust, and the high luminosity and proximity to the stellar surface will cause strong irradiation, and therefore heating \citep{spiegelJupiterWillBecome2012}. The mass-loss from the stellar winds can adiabatically expand a planet's orbit \citep{jeansCosmogonicProblemsAssociated1924}, potentially destabilizing the orbit and chaotically ejecting the planet \citep{kratterStarHoppersPlanet2012}. Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}. When combined with adiabatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.

Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions. \citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around another star (or, in fact, the whole system). These disks serve as reservoirs of material and energy for planet formation, which could be kick-started by a first-generation planet acting as a seed. Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both gravitational-instability (``hot start'') and core-accretion (``cold start'') formation theories \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}. Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies. \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI). \citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted three-body problem and concluded up to $\sim$10\% of all white dwarf binaries might contain ``star-hopper'' planets which migrate between the stars.

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. Recent evidence and theoretical works \citep[e.g.,][]{xuSpitzerObservationsWhite2012,koesterFrequencyPlanetaryDebris2014,verasPostmainsequencePlanetarySystem2016,vanderburgGiantPlanetCandidate2020}, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets. These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.

Direct imaging is well-suited for finding planets around white dwarfs due to the intrinsic faintness of the host (compared to a MS star) and lack of spectral features for radial velocity studies \citep{burleighImagingPlanetsNearby2002a}. With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband spectral-energy distribution analysis or transit photometry methods. High-contrast imaging pushes direct imaging to its limits using large-aperture telescopes, adaptive optics, coronagraphy, low-noise detectors, image-processing, and observational techniques. Despite the power of high-contrast imaging, very few observations have been carried out for white dwarfs (a recent example is \citealt{pathakHighContrastImaging2021}).

Exoplanets are faint enough that in certain cases only a few photons per second reach the detector. Host stars are typically many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$), and planets have very small angular separations from their hosts, which makes it difficult to disentangle the planet-light from the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}. In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-static perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}). Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation. AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.

Typical high-contrast targets are nearby young objects observed in the near-infrared. Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010} and observing them in the near-infrared corresponds with their peak blackbody emission. Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the planet from the star. Nearby targets are also intrinsically brighter, enabling effective AO control. White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced star-planet flux ratio. In addition, a post-MS planet would be much younger than the system age of a white dwarf and would therefore still retain a large portion of its latent heat, further motivating high-contrast searches of nearby white dwarfs.

In this work we set out to perform high-contrast observations of Sirius B to search for post-MS planets. In the rest of this report, we will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems, as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).

@@

The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a $J=$-1.36 magnitude A1V star, and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}. As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date. Their astrometric uncertainties are over an order of magnitude improved from the visual orbit derived by \citet{vandenbosOrbitSiriusADS1960}. Following the procedure of \citet{gatewoodStudySirius1978}, \citet{bondSiriusSystemIts2017} derived dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculated the longest stable companion period around Sirius B to be \qty{1.8}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

The total age of Sirius B is the combination of its white dwarf cooling age and the time from the zero-age main sequence (ZAMS) to the tip of the giant branch (TGB). We adapt the cooling age derived by \citet[Sec.~8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}. We use the updated white dwarf initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.

We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}. These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model. The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}. Determining stellar ages is challenging, and the age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%). The values for our adapted and derived parameters are compiled in \Cref{tbl:system}.

One of the peculiarities of the Sirius system is its large eccentricity, $e\sim0.6$ \citep{bondSiriusSystemIts2017}. If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
\begin{equation}
    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
\end{equation}
where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states \citep{jeansCosmogonicProblemsAssociated1924}. The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}. If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution. In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}. \citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate-mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}. This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage. Mass transfer and tidal circularization would be expected; however, the present-day eccentricity provides contrary evidence.

\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary. \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of a third body between \qtyrange{0.6}{5.5}{\solarmass}. \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is a collision with one of the binary components. If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig. 7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture. This is an interesting, although uncertain, explanation for the peculiar surface chemical abundances found on Sirius A \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}. The variety in these studies shows the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.

@@

\begin{figure}
    \centering
    \epsscale{1.2}
    \plotone{spike}
    \caption{Scattered light from Sirius A is present in our FOV around Sirius B as shown by this diffraction spike  sweeping across a calibrated science frame of Sirius B from the first epoch. Despite Sirius B's separation of \ang{;;11}, the overwhelming brightness of Sirius A impedes observations of Sirius B.}
    \label{fig:spike}
\end{figure}

@@

\subsection{Pre-processing}\label{sec:pre-processing}

>>>>

% custom SI units
\DeclareSIUnit\parsec{pc}
\DeclareSIUnit\au{AU}
\DeclareSIUnit\jupitermass{M_J}
\DeclareSIUnit\milliarcsecond{mas}
\DeclareSIUnit\solarmass{M_\odot}
\DeclareSIUnit\year{yr}
\DeclareSIUnit\pixel{px}
\sisetup{
    list-units=single,
    separate-uncertainty
}

@@

@@

\title{An Imaging Search for Post-MS Companions of Sirius B}

\shorttitle{An Imaging Search for Post-MS Companions of Sirius B}
\shortauthors{Lucas et al.}

@@

\begin{abstract}
Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution. We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-MS planetary evolution in the Sirius system. We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. Our observations are contrast limited out to \qty{1}{\au} and background limited beyond. The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} absolute magnitude. We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids. We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}. Consistent with previous results, we do not detect any companions around Sirius B. Our excellent detection limits, even without coronagraphy, demonstrate the capabilities for modern high-contrast imaging studies of nearby (\textless\qty{25}{\parsec}) white dwarfs.
\end{abstract}

@@

In recent decades astronomers have discovered thousands of exoplanets orbiting stars that will eventually evolve into giants and then white dwarfs \citep{akesonNASAExoplanetArchive2013}. The fate of planets around these stars beyond the main-sequence (MS) is uncertain due to the large expansion, stellar winds, and high irradiation encountered on the giant branch \citep{verasPostmainsequencePlanetarySystem2016}. Despite this, direct evidence from white dwarf (WD) pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought. Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.

The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs. As the MS star runs out of hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius. When helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation. Eventually the star will run out of fuel and conclude its nuclear burning and become a WD. The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Surviving planets are subject to adiabatic orbit expansion, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}. The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.

Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions. \citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where in multi-star systems the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system). Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with ``hot-start'' planetary formation timescales \citep{spiegelSpectralPhotometricDiagnostics2012a}. A first-generation planet could act as a seed for planetesimal growth in these disks, too. Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies. \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI). \citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted 3-body problem and concluded up to $\sim$10\% of all WD binaries might contain ``star-hopper'' planets which migrate between the stars.

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade. In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}). We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).

\section{Directly imaging post-MS systems}\label{sec:imaging}

High-contrast imaging is a powerful technique for discovering and characterizing exoplanets. Directly imaging a circumstellar companion is difficult, though. The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources. Thermal emission from exoplanets peaks well into the infrared, on the Rayleigh-Jeans limit of the stellar spectrum. This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.

WDs are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their MS progenitors which reduces the contrast necessary to detect a companion. The high effective temperatures of WD photospheres pushes the peak thermal emission even further into the optical and ultraviolet, reducing the intrinsic contrast between the star and the planet. In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique. The small stellar radii of WDs lowers the transit probability significantly, although detections of substellar companions around WDs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}. The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby WDs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.

% \section{Post-MS evolution}\label{sec:post-ms}

% There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. The expansion of the stellar photosphere will engulf companions and cause tidal interactions, destroying planets or disrupting their orbits \citep{burleighImagingPlanetsNearby2002a, nordhausOrbitsLowmassCompanions2013}. Planets that escape engulfment will encounter stellar winds and strong irradiation, causing orbital expansion \citep{jeansCosmogonicProblemsAssociated1924}, enriching the circumstellar environment with metals and dust, and strongly heating planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.

% The observational evidence for planets in post-MS systems is varied. WD atmospheres quickly separate heavy elements in their atmospheres due to their high surface gravity \citep{schatzmanTheorieDebitEnergie1945}, which causes the elements to sink and stratify. The time scale for this phenomena can be days to $\sim$\qty{1}{\mega\year}, significantly shorter than WD cooling ages, which means that most WD atmospheres are comprised of hydrogen, helium, and some carbon. However, metals heavier than carbon have been detected in WDs with cooling ages between \qtyrange{30}{500}{\mega\year}. A common explanation for the ``pollution'' of these WDs is the accretion of planetary material. This is backed up by the evidence of WD debris disks, although only a fraction of all polluted WDs are host to a disk \citep{koesterFrequencyPlanetaryDebris2014}. Chemical analysis shows the pollution is closer to planetary in origin rather than the interstellar medium. Most damning, though, is the correlation between the relative population of polluted WDs (25\% - 50\%) and the expected number of MS planet hosts \citep{koesterFrequencyPlanetaryDebris2014}.

% suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase. Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}. During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet . In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.

% The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}. \citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

% Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf. \citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

@@

One fascinating target for post-MS observations is Sirius B, the closest and brightest WD to our solar system. The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for direct imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius, to date. They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

The total age of Sirius B is the combination of its WD cooling age and the time from the zero-age MS (ZAMS) to the tip of the giant branch (TGB). We adapt the cooling age derived by \citet[sec. 8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}. We use the updated WD initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.

We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}. These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model. The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}. An age uncertainty of $\sim$4\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all. These values are compiled in \Cref{tbl:system}.

One of the peculiarities of the Sirius system is its large eccentricity of 0.59 \citep{bondSiriusSystemIts2017}. If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
\begin{equation}
    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
\end{equation}
where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states \citep{jeansCosmogonicProblemsAssociated1924}. The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}. If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution. In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}. \citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}. This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage. Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.

\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping'', but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which we would expect to increase with mass transfer to conserve total angular momentum in the binary. \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}. \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components. We extrapolate their Figure 7 using the parameters for Sirius to estimate a $\sim$70\% collision probability for an initial companion of Sirius B if it is chaotically ejected. When combined, these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.

@@

% \begin{deluxetable}{ccccc}
%     \tabletypesize{\small}
%     \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
%     \label{tbl:obs}}
%     \tablehead{
%         \colhead{Epoch} &
%         \colhead{2020-02-4} &
%         \colhead{2020-11-21} &
%         \colhead{2020-11-28} &
%         \colhead{}
%     }
%     \startdata
%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
%     \enddata
% \end{deluxetable}

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{spike}
    \caption{Scattered light from Sirius A is present in our FOV around Sirius B as shown by this diffraction spike  sweeping across a calibrated science frame of Sirius B from the first epoch. Despite Sirius B's separation of \ang{;;11}, the overwhelming brightness of Sirius A impedes observations of Sirius B.}
    \label{fig:spike}
\end{figure}

@@

\subsection{Pre-processing}
